Prefetching SPARQL query cacher

### 2016-05-03 dissertation/cache-proxy.tex
more on the proxies

@@

\draw [->] (0.2,4) --(0.2,0);
\draw [<-] (0.4,4) --(0.4,0);
\draw [->] (0.7,2) --(0.7,0);
\draw [<-] (0.9,2) --(0.9,0);
\draw [->] (1.2,4) --(1.2,2);
\draw [dashed, ->] (1.2,2) --(1.2,0);
\draw [dashed, <-] (1.4,2) --(1.4,0);
\draw [->] (1.5,2) --(1.5,4);
\draw [->] (1.7,2) --(1.7,0);
\draw [<-] (1.9,2) --(1.9,0);
\draw [->] (2.2,4) --(2.2,2);
\draw [->] (2.4,2) --(2.4,4);
\end{tikzpicture}
\caption{The possible positions of a cache. A cache may reside at both
  the server side (as a database cache) or client side, or any of the
  intermediate proxies. The database cache and reverse proxy is
  typically controlled by the data provider. The arrows illustrate
  requests (when pointing down) and responses (when pointing up) in a
  deployment scenario for when a the query cache considered in this
  paper is deployed on a caching proxy in the Internet infrastructure,
  see the text for details.}
\end{center}
\end{figure}

>>>>

Figure~\ref{fig:messaging} illustrates where caches may be in the
Internet infrastructure, as well as HTTP requests and responses in a
typical deployment scenario of the system.

@@

\draw [->] (0.2,4) --(0.2,0);
\draw [<-] (0.4,4) --(0.4,0);
\draw [->] (0.7,2) --(0.7,0);
\draw [<-] (0.9,2) --(0.9,0);
\draw [->] (1.2,4) --(1.2,2);
\draw [dashed, ->] (1.2,2) --(1.2,0);
\draw [dashed, <-] (1.4,2) --(1.4,0);
\draw [->] (1.5,2) --(1.5,4);
\draw [->] (1.7,2) --(1.7,0);
\draw [<-] (1.9,2) --(1.9,0);
\draw [->] (2.2,4) --(2.2,2);
\draw [->] (2.4,2) --(2.4,4);
\end{tikzpicture}
\caption{The possible positions of a cache. A cache may reside at both
  the server side (as a database cache) or client side, or any of the
  intermediate proxies. The arrows illustrate requests (when pointing
  down) and responses (when pointing up) in a deployment scenario for
  when a the query cache considered in this paper is deployed on a
  caching proxy in the Internet infrastructure, see the text for
  details.}\label{fig:messaging}
\end{center}
\end{figure}

The system is based on HTTP, which implies a client-server
architecture. In this architecture, a cache may be present at
conceptually five different levels. First, the client may have its own
cache, which caches only responses made by the client itself. The next
level is known as a forward proxy. They aren't currently very common,
but have in the past often been institutional proxies, or proxies
employed by Internet Service Providers for caching responses that may
be common to many of their users. The next level, generically referred
to as a caching proxy, may be in the Internet
infrastructure. Currently, the most common form of this type of proxy
is known as a Content Delivery Network (CDN). It is very common to
have a reverse proxy near the server. They are often known as a ``Web
Accelerator''. Usually, they will communicate with the server with
HTTP, but it is conceivable that it may use a different protocol, and
may employ detailed knowledge of the hosted data to optimise cache
operations. Finally, the database, in this context a SPARQL Endpoint,
may use conventional database caching techniques. The database cache
and reverse proxy is typically controlled by the data provider.

The present system may be deployed at any of these levels. However,
since the database and the reverse proxy in front of it may have
detailed knowledge of the data, e.g. a complete data profile with
statistics to optimise join order, these levels have much in common
with a conventional database cache, which is extensively discussed in
the literature.

My interest is the case where the caching proxy has no further
knowledge of the data than what is exposed through the SPARQL
Endpoint or hypermedia metadata. In practice, there is very
little information.
